\chapter{Project Planning}
\section{Planned Phases of the Project}
The project is split up into a number of phases, each of which must be completed sequentially. During these phases the interim report and final report will be developed as a skeleton in parralell.
\begin{enumerate}
	\item Research - This phase consists of finding and reading existing literature. It is at this time that the project idea is developed fully.
	\item Simple Implementation - In this phase, a proof of concept implementation will be deveolped. It will entail a simple swarm learning algorithm learning on a basic dataset, without any complex problems. This implementation will be build upon in further phases.
	\item Interim Report - This phase is focussed on filling out and finalising the interim report.
	\item Main development - In this phase, the iterative development of the swarm learning algorithm will occur. This is actually a repetition of four sub-phases:
	\begin{enumerate}
		\item Further research on real-world problem
		\item Implement real-world problem and test current solution
		\item Implement mitigations and test / evaluate
		\item Document any discoveries and evaluations of mitigations
	\end{enumerate}
	\item Final report - In this phase, the final report will be written up.
	\item Housekeeping - This is the final phase wihch is used for any extra jobs that were not able to be completed in other phases.
\end{enumerate}
\section{Completed Work}
INSERT GANT CHART HERE
\section{Remaining Work}
INSERT GANT CHART HERE